Argennon: A Scalable Smart Contract Platform

### 2021-06-06 tex/sections/avm.tex
Describe the AVM standard library
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

>>>>

As we explained in Section~\ref{subsec:method-invocation} by using \texttt{invoke\_internal} instruction, a smart
contract can invoke methods of another smart contract in its own context. This is how AVM smart contracts
invoke methods of the AVM standard library. Methods of the AVM standard library are stored
with the \texttt{applicationID} zero in the AVM method area. This implies that the AVM standard library is actually
a part of the root smart contract.

In Argennon, the root smart contract is an updatable smart contract, which can be updated by the Argennon consensus
protocol. This means that bugs or security vulnerabilities in the AVM standard library could be quickly patched and
smart contracts can use the AVM standard library safely. Many important and useful functionalities,
such as fungible and non-fungible assets, access control mechanisms,
and general purpose DAOs are implemented in the Argennon standard library.

All Argennon standards, for instance ARC standard series, which defines standards regarding transferable assets,
are defined based on how a contract should use the AVM standard library. As a result, Argennon standards are
different from conventional blockchain standards. Argennon standards define some type of standard logic and
behaviour for a smart contract, not only a set of method signatures. This enables users to expect certain type
of behaviour from a contract which complies with an Argennon standard.
